\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Subrata Halder}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{www.subratahalder.me}
% vs how you want it to show up. If it's the same you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://www.subratahalder.me/}
\newcommand{\yourEmail}{subrata797979@gmail.com}
\newcommand{\yourPhone}{+918777047822}
\newcommand{\githubUserName}{subrata797979}
\newcommand{\linkedInUserName}{subratahalder97}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    % $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
\educationHeading{MCA}{Maulana Abul Kalam Azad University of Technology (MAKAUT)}{Kalyani Government Engineering College, ON}{2019 - 2022}

%\teacherAssistant{World Wide Web Information Systems Development}
%\courseWork{DSA; OOP with Java; DBMS I; DBMS II; C; C++; Software Engineering and TQM; Computer Networks; Business Management; Unix and Shell Programming}
\sectionsep

% Put school first and degree second if your school is reputable
\educationHeading{BSc. Honours Computer Science}{West Bengal State University (WBSU)}{Barrackpore Rastraguru Surendranath College, ON}{2015 - 2018}

%\teacherAssistant{World Wide Web Information Systems Development}
%\courseWork{C; C++; DBMS; CN; Shell, Microprocessor, Computer Organization and Architecture}
\sectionsep


%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Experience}
\resumeHeading{Codearts Solution Pvt Ltd}{Jr. Developer Trainee}{Kolkata, ON}{Aug 2022 –  Jan 2023}
\begin{bullets}
    \item Developed multiple components of \textbf{ERM i.e. Employee Resource Management System}, an internal product of Codearts Solution Pvt. Ltd. like \textbf{Holiday Module, Notice Module, Chat Module} etc. in \textbf{PHP, MYSQL, HTML, CSS, JS, JQUERY, BOOTSTRAP} both frontend and backend with \textbf{AJAX calls and PHP SESSIONS} maintaining PR on daily basis using \textbf{GIT and GITHUB}. 
    \item Worked on \textbf{Wordpress Theme Development, Content Management, Wocommerce} etc. helping multiple clients like \textbf{KMG Import, IRON CURTAIN CUSTOMS, Hair Doctor NYC} etc.
\end{bullets}
\sectionsep

\resumeHeading{Codeaxes Digital Solutions}{Jr. Full Stack Engineer Intern}{Delhi, ON}{Nov 2021 – Dec 2021}
\begin{bullets}
    \item Developed dashboard functionality on top of \textbf{AdminLTE3} using \textbf{Angular} and \textbf{TypeScript} fetched from \textbf{Node} backend through custom \textbf{REST API} endpoints to visualize data stored in \textbf{MongoDB} ensuring proper authentication and authorization using \textbf{JWT} reporting \textbf{PR} on daily basis using \textbf{Git} and \textbf{Bitbucket}.
\end{bullets}
\sectionsep

\resumeHeading{Air King Group}{Digital Curator Intern}{Kolkata, ON}{Sep 2021 - Nov 2021}
\begin{bullets}
    \item Developed new design and ideas on daily basis in form of \textbf{Poster}, \textbf{Banner}, \textbf{Brochure}, \textbf{Social Media Post}.
\end{bullets}
\sectionsep


%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Professional Projects}

\projectHeading{Codearts ERM}{https://github.com/RinikaDey/codearts-ERM}{Html, Css, Javascript, Bootstrap, PHP, Mysql}
A \textbf{Employee Management System} i.e. ERM for managing all modules like, employee profile, leave, holiday, timesheet, gracetime, notice, access log etc.
\textit{(Associated with \textbf{Codearts Solution Pvt Ltd})} 
\sectionsep

\projectHeading{Wordpress Custom Theme}{https://github.com/RinikaDey/wordpress_database}{Wordpress, PHP, Mysql, Html, Css, Bootstrap}
Developed many \textbf{custom themes} according to user requirements.
\textit{(Associated with \textbf{Codearts Solution Pvt Ltd})} 
\sectionsep
  
\projectHeading{Xconnect Module of KGEC-IMS}{https://github.com/subrata797979/xConnect}{Html, Css, Javascript, Bootstrap, PHP, Mysql}
A module that \textbf{searches, filters and communicate students and ex-students} with modular UI/UX.
\textit{Under the guidance of \textbf{Dr. Partha Garai} associated with KGEC (MCA)} 
\sectionsep

\projectHeading{College Gate}{https://github.com/subrata797979/21_CollegeGate}{Html, Css, Javascript, Bootstrap, PHP, Mysql}
A website \textbf{recommending suitable college} after Higher Secondary without.
\textit{Under the guidance of \textbf{Professor Phulen Mahato} associated with BRSNC (BSc Hons.)} 
\sectionsep

%\href{https://www.hackerrank.com/subrata797979}{5* Java \underline{Hackerrank} with 9 certifications}

\section{Personal Projects}

\projectHeading{Book Management System}{https://github.com/subrata797979/42_Book_Management_Backend}{Node, Express, MongoDB, Angular, MEAN Stack}
A \textbf{node} backend with \href{https://github.com/subrata797979/41_Book_Management_Frontend}{separate \textbf{angular} \underline{frontend}} with \textit{\textbf{chart js}} for visualization.\\
\sectionsep

\projectHeading{CollegeGate Revamped}{https://github.com/subrata797979/CollegeGateRevampedBackend}{Java, Spring MVC, Maven, Spring Boot, Angular Frontend}
A revamped version of my BSc. final year project in \textbf{Java Spring Boot} with \href{https://github.com/subrata797979/CollegeGateRevampedFrontend}{separate \textbf{angular} \underline{frontend}}.\\
\sectionsep
  

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \singleItem{Languages:}{Java, C, C++, Python, PHP, Bash, SQL}
    \\
    \singleItem{Web Development:}{JavaScript, Angular, TypeScript, Node, HTML/CSS/Bootstrap}
    \\
    \singleItem{Technology:}{Java Spring Boot, MEAN Stack, Postman, Git, Linux, \LaTeX, MongoDB, phpMyAdmin, Android Development}
    \\
    \singleItem{Achievement:}{\href{https://www.hackerrank.com/subrata797979}{5* Java \underline{Hackerrank} with 9 certifications},\href{https://leetcode.com/subrata797979/}{ 300+ \underline{Leetcode} Solved},\href{https://drive.google.com/file/d/12bhO9nzDUkLcGOSTJybPe6MhMqX_wprU/view}{ 73.83\% TCS \underline{NQT}}}
\end{skillList}

\end{document}